Meta-analysis

### 2019-11-19 191115_PMMB_DataWrangling_PM.Rmd
missen flats wrangled

>>>>

### Missen Flats 2017
```{r Missen2017}
# ____________________________________________________________
# _____________   Missen Flats (Fogarty's) 2017     ____________
Fogerty_17 <-
   read.xlsx(
      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2017/MissenFlats/Fogerty Work File 2017 (Autosaved).xlsx",
      sheet = "Data",
      startRow = 3,
      colNames = TRUE,
      detectDates = TRUE
   )[, 1:43]

#dim(Fogerty_17)   # 162 rows , 43 Columns

# Columns to keep
Fogerty_17 <- Fogerty_17[, c('Plot', 'Rep', 'Row', 'Column', 'Chem.Trt',
                           'Chemical', 'Row.Spacing.(m)', 'Treatment.No',
                           'Treatment', 'Population.plsnts/ha',
                           '2017-03-07', '2017-03-19', '2017-03-24',
                           '2017-04-02', '2017-04-10', '2017-04-18',
                           'Yield.t/ha', 'Grain.Moisture.%', 'Temp.moisture.Taken',
                           '100.grain.wt.Grams')]

Fogerty_17$Treatment.No <- as.numeric(unlist(strsplit(
   Fogerty_17$Treatment.No, "T"))[
      seq(from = 2, to = 324, by = 2)])

# Fog_17_sum <- Fogerty_17 %>%
#    group_by(Treatment, Chemical, `Row.Spacing.(m)`) %>%
#    summarise(
#       m_disease = mean(`2017-04-18`, na.rm = TRUE),
#       sd_disease = sd(`2017-04-18`, na.rm = TRUE),
#       m_Yield = mean(`Yield.t/ha`, na.rm = TRUE),
#       sd_Yield = sd(`Yield.t/ha`, na.rm = TRUE)
#    )
# 
# write.csv(
#    Fog_17_sum,
#    "C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/Fogerty_17_mean.csv"
# )
# 
# 
# # gather the incidence assessment into long format
# Fogerty_17.1 <-
#    gather(Fogerty_17,
#           key = Incidence_assessment_date,
#           value = Incidence,
#           colnames(Fogerty_17)[c(11:16)])
# #Fogerty_17.1$Severity <- gather(Fogerty_17, key = assessment_date, value = Severity,
# #                                colnames(Fogerty_17)[c(15,18)])
# Fogerty_17.1$location <- "Fogerty"
# 
#

head(Fogerty_17)
unique(Fogerty_17$Chem.Trt)
unique(Fogerty_17$Chemical)
Fogerty_17[,7:11]
```

#### Define treatment data
```{r King16_treatmentDefine}
Fogerty_17_dat <- Fogerty_17 %>%
   mutate(trade_name = 
             case_when(Chem.Trt == 1 ~ "Folicur",
                       Chem.Trt == 2 ~ "Throttle",
                       Chem.Trt == 3 ~ "Custodia",
                       TRUE ~ "other"))%>%
   mutate(fungicide_ai = 
             case_when(Chem.Trt == 1 ~ "tebuconazole",
                       Chem.Trt == 2 ~ "propiconazole",
                       Chem.Trt == 3 ~ "200 g/L tebuconazole + 120 g/L azoxystrobin",
                       TRUE ~ "other"))%>%
   mutate(dose_ai.ha = 
             case_when(Chem.Trt == 1 ~ 62,
                       Chem.Trt == 2 ~ 125,
                       Chem.Trt == 3 ~ 60,
                       TRUE ~ 9999))%>%
   mutate(fungicide_application_1 = 
             case_when(Treatment.No == 1 ~ as.Date(NA),
                       Treatment.No == 2 ~ as.Date("2017-02-22", format = "%Y-%m-%d"),
                       Treatment.No == 3 ~ as.Date("2017-03-08", format = "%Y-%m-%d"),
                       Treatment.No == 4 ~ as.Date("2017-03-08", format = "%Y-%m-%d"),
                       Treatment.No == 5 ~ as.Date("2017-03-19", format = "%Y-%m-%d"),
                       Treatment.No == 6 ~ as.Date("2017-03-08", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_2 = 
             case_when(Treatment.No == 4 ~ as.Date("2017-03-24", format = "%Y-%m-%d"),
                       Treatment.No == 6 ~ as.Date("2017-04-02", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(spray_n = 
             case_when(Treatment == 1 ~ 0,
                       Treatment == 4 ~ 2,
                       Treatment == 6 ~ 2,
                       TRUE ~ 1))

#### Input trial data
```{r King16_Trialdat}
# Remove zeros
Fogerty_17_dat[Fogerty_17_dat$`2017-03-07` == 0 ,c("2017-03-07")] <- 1

Fogerty_17_dat <- 
   data.frame(trial_ref = "mung1617/02",
              year = "2016",
              location = "Missen Flats",
              host_genotype = "Jade",
              trial_design = "RCB",
              plot_length = 10,
              plot_width = 2,
              plant_density = Fogerty_17_dat$`Population.plsnts/ha`,
              row_spacing = Fogerty_17_dat$`Row.Spacing.(m)`,
              replicate = Fogerty_17_dat$Rep,
              planting_date = as.Date("2017-01-27", format = "%Y-%m-%d"),
              emergence_date = as.Date("2017-02-01", format = "%Y-%m-%d"),
              flowering_date = as.Date(NA),
              pod_fill_date = as.Date(NA),
              mid_late_pod_fill = as.Date(NA),
              first_sign_disease = as.Date("2017-03-07", format = "%Y-%m-%d"),
              trade_name = as.factor(Fogerty_17_dat$trade_name),
              fungicide_ai = Fogerty_17_dat$fungicide_ai,
              dose_ai.ha = Fogerty_17_dat$dose_ai.ha,
              n_treatment = as.numeric(Fogerty_17_dat$Treatment.No),
              fungicide_application_1 = Fogerty_17_dat$fungicide_application_1,
              fungicide_application_2 = Fogerty_17_dat$fungicide_application_2,
              total_fungicide = Fogerty_17_dat$spray_n,
              harvest_date = as.Date("2017-05-11", format = "%Y-%m-%d"),
              final_assessment = as.Date("2017-04-18", format = "%Y-%m-%d"),
              PM_final_severity = Fogerty_17_dat$`2017-04-18`,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(Fogerty_17_dat$`Yield.t/ha`),
              AUDPC = apply(Fogerty_17_dat[,c("2017-03-07", "2017-03-19", "2017-03-24", "2017-04-02","2017-04-10","2017-04-18")]-1,1, 
                            FUN = audpc, dates = c(1,12,17,26,34,42)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
              )
```

#### Calculating treatment means
```{r Missen17_means}

Fogerty_17_m <- Fogerty_17_dat %>%
   group_by(host_genotype, n_treatment, row_spacing, fungicide_ai) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             dose_ai.ha = unique(dose_ai.ha),
             trial_ref = unique(trial_ref),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = mean(plant_density, na.rm = TRUE),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = unique(emergence_date),
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
             meanSq = anova(lm(grain_yield.t.ha. ~ factor(n_treatment) + fungicide_ai + row_spacing, data = subset(Fogerty_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
   )

# For some weird reason standard deviations are comming back NA in the code above
Fogerty_17_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
   Fogerty_17_dat %>%
   group_by(n_treatment, row_spacing, fungicide_ai) %>%
   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
   select(c("disease_error","yield_error"))

write.csv(
   Fogerty_17_m,
   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2017/MissenFlats/Fogerty_17_mean.csv",
   row.names = FALSE
)
